Appendix

### 2020-06-21 manuscript/article.tex
add table 3

\begin{table}[htpb]
\footnotesize
\caption{Meta Regression Results}
\label{tab:regressions}
\centering
\begin{tabular}{lcccccc}
\toprule
\midrule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Expenditure Per Capita} & \multicolumn{2}{c}{Log Expenditure Per Capita} & \multicolumn{2}{c}{Gov. Spending \% GDP} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7}
& Restricted & Extended & Restricted & Extended & Restricted & Extended \\
\midrule
Intercept & -104.07 & -296.907 & 8.959 & -1.574 & 2.669 & -10.11 \\
 & (318.93) & (166.687)$\dagger$ & (47.644) & (15.883) & (2.04) & (5.8586)$\dagger$\\
%
Independent Variable: $N$ & -2.924 & -5.447 & 0.164 & -0.009 & -0.0094 & -0.0015\\
 & (2.093) & (0.969)*** & (0.326) & (0.126) & (0.006) & (0.005)\\
%
Independent Variable: log($N$) &  &  &  &  & -0.011 & 0.038\\
 &  &  &  &  & (0.019) & (0.0195)$\dagger$\\
%
Year & 0.052 & 0.15 & -0.004 & 0.001 & -0.000 & 0.006\\
 & (0.159) & (0.083)$\dagger$ & (0.024) & (0.008) & (0.001) & (0.003)*\\
%
Published: No &  &  & -0.152 & -0.083 & 0.0633 & 0.113 \\
 &  &  & (0.19) & (0.073) & (0.016)* & (0.026)***\\
%
Non-Majoritarian (PR \& Mixed) & 0.346 & 1.024 & &  & -2.0556 & -2.163\\
 & (1.553) & (0.77) & &  & (0.3260)** & (0.163)***\\
%
Method: Panel & 1.457 & -0.142 & 0.258 & -0.244 & 0.0557 & 0.126\\
 & (2.238) & (0.814) & (0.189) & (0.0147)* & (0.0071)* & (0.032)***\\
%
Method: IV & 1.494 & 0.191 &  &  &  & \\
 & (2.668) & (0.822) &  &  &  & \\
%
Method: RDD &  &  &  &-0.298&  & \\
 &  &  &  & (0.066)*** &  & \\
% 
\bottomrule
\end{tabular}
\begin{minipage}{\textwidth}
\renewcommand{\footnoterule}{}
\footnotetext{\textbf{Note:} {The restricted and extended samples include 36 and 126 study coefficients, respectively. Reference categories: Independent Variable $= k$; Published $= Yes$; Non-Majoritarian (PR \& Mixed) $= Majoritarian$; Method $= OLS$. Significance codes: *** $p < 0.001$; ** $p < 0.01$; * $p < 0.05$; $\dagger$ $p < 0.1$.}}
\end{minipage}
\end{table}

@@

Several variables are statistically significant in the last set of
meta-regressions. The dependent variable is public expenditures as a percentage
of GDP. In both restricted and extended samples we find that unpublished papers
tend to have higher coefficients than published papers. In contrast with our
previous results, we also see that passing from OLS to panel/fixed effects and
from majoritarian to non-majoritarian electoral systems increase the detected
coefficients. We also see that year has a positive effect on the outcome: the
newer the publication, the higher the detected coefficient. However, the
result is statistically significant only in the extended sample. Finally,
studies with $n$ as an independent variable have lower coefficients than those
that analyse $k$, what is consistent with our previous meta-regressions.

>>>>

\begin{table}[htpb]
\footnotesize
\caption{Meta Regression Results}
\label{tab:regressions}
\centering
\begin{tabular}{lcccccc}
\toprule
\midrule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Expenditure Per Capita} & \multicolumn{2}{c}{Log Expenditure Per Capita} & \multicolumn{2}{c}{Gov. Spending \% GDP} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7}
& Restricted & Extended & Restricted & Extended & Restricted & Extended \\
\midrule
Intercept & -117.987 & -300.789 & -7.363 & -8.296 & 2.851 & 2.507\\
          & (203.717) & (157.555)* & (25.458) & (12.037) & (1.778) & (2.467)$\dagger$\\
%
Independent Variable: $N$ & -2.307 & -5.347 &  -0.280 &  -0.0577 &-0.009 & 0.003\\
                          & (1.490)$\dagger$ & (0.929)*** & (0.162) & (0.073) & (0.005)$\dagger$ & (0.005)\\
%
Independent Variable: log($N$) &  &  &  &  &-0.011& 0.002\\
                               &  &  &  &  & (0.001) & (0.014)\\
%
Year & 0.059 & 0.152 &  0.004 &  0.004 &-0.000& -0.000\\
     & (0.101) & (0.078)* & (0.013) & (0.006) & (0.001) & (0.001)\\
%
Published: No &  &  & 0.200 &  0.103 & 0.0625 & 0.060\\
              &  &  & (0.127) & (0.065) & (0.014)* & (0.016)*\\
%
Non-Majoritarian (PR \& Mixed) & 0.428 & 0.985 & &  & -2.055 & -2.169\\
                               & (0.827) & (0.723)$\dagger$ & &  & (0.283)** & (0.166)***\\
%
Method: Panel & 1.203 & -0.135 & 0.188 & -0.252 & 0.055 & 0.058\\
              & (1.575) & (0.797) & (0.093) & (0.068)*** & (0.013)* & (0.017)*\\
%
Method: IV & 1.317 & 0.186 &  &  &  & \\
           & (1.807) & (0.802) &  &  &  & \\
%
Method: RDD &  &  &  &-0.285&  & \\
            &  &  &  & (0.062)*** &  & \\
% 
\bottomrule
\end{tabular}
\begin{minipage}{\textwidth}
\renewcommand{\footnoterule}{}
\footnotetext{\textbf{Note:} {The restricted and extended samples include 36 and 126 study coefficients, respectively. We report the results from the permutation tests. Reference categories: Independent Variable $= k$; Published $= Yes$; Non-Majoritarian (PR \& Mixed) $= Majoritarian$; Method $= OLS$. Significance codes: *** $p < 0.001$; ** $p < 0.01$; * $p < 0.05$; $\dagger$ $p < 0.1$.}}
\end{minipage}
\end{table}

%% CONFERIR TODOS OS RESULTADOS

@@

Several variables are statistically significant in the last set of
meta-regressions. The dependent variable is public expenditures as a percentage
of GDP. In our restricted sample, we see that studies with $n$ as an
independent variable have lower coefficients than those that analyse $k$, what
is consistent with our previous models. Both models also show that unpublished
papers tend to have higher coefficients than published papers. Regarding the
electoral systems, see that passing from majoritarian to non-majoritarian
decrease overall levels of public spending. Finally, we find that models
estimated with panel data have larger values than those modelled with OLS.
